Pre-Analysis Plan: Bend or Break? Experimental Evidence of Voters' Punishment for Striking Political Compromises

### 2021-04-22 docs/pap/compromise-punishment-pap.Rmd
finalize pap

**Gender hypothesis** (_H1_):  Women politicians are evaluated lower when striking a political compromise compared to men politicians.

@@

**Intersection hypothesis** (_H3_): Women politician with a migration background are evaluated lower when striking a political compromise compared to men politicians without a migration background.

>>>>

**Gender hypothesis** (_H1a_):  Women politicians are evaluated lower when striking a political compromise compared to men politicians.

**Gender hypothesis** (_H1b_):  Women politicians are evaluated lower when not striking a political compromise compared to men politicians.

@@

**Intersection hypothesis** (_H3a_): Women politician with a migration background are evaluated lower when striking a political compromise compared to men politicians without a migration background.

**Intersection hypothesis** (_H3b_): Women politician with a migration background are evaluated lower when not striking a political compromise compared to men politicians without a migration background.
